### 2022-08-24 README.Rmd
bump to 1.7.0.9000
pdf vignette updated

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

@@

# Test of no treatment effect
lhs <- matrix(c(1, -1, 0, 0,
                0, 1, -1, 0,
                0, 0, 1, -1), byrow = TRUE, nrow = 3)
elt(fit3, lhs = lhs)
```

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  dpi = 300,
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

@@

# Test of no treatment effect
contrast <- matrix(c(
  1, -1, 0, 0,
  0, 1, -1, 0,
  0, 0, 1, -1
), byrow = TRUE, nrow = 3)
elt(fit3, lhs = contrast)
```
